Reproducible development environments with rix

### 2023-12-13 paper.qmd
started talking about rig

>>>>

The next step in reaching the gold standard of reproducibility would be to not only
install the right packages used for the analysis, but also the right version of
[R]{.proglang}. Of course, it would be possible to install the right version manually,
but here too, there are tools that simplify the process such as @rlib2023.
